### 2022-11-15 chapter1.tex
Added additional details to gene clustering section

\subsection*{Grouping orthologous groups by gene}
As genes can have several annotated isoforms, each gene can be associated with several orthologous groups. However, the orthologous groups are not organized into gene-level units since they were clustered using sequence similarity only. A graph-based approach was therefore used to group orthologous groups with similar sets of parent genes. First, a gene overlap graph was constructed by defining an edge between orthologous groups if the intersection of their associated sets of parent genes is at least 50\% of the smaller of the two. Gene groups were then taken as the connected components of the resulting graph.
% TODO: More description about results of this step

>>>>

\subsection*{Grouping orthologous groups by gene}
As genes can have several annotated isoforms, each gene can be associated with several orthologous groups. However, the orthologous groups are not organized into gene-level units since they were clustered using sequence similarity only. A graph-based approach was therefore used to group orthologous groups with similar sets of parent genes. First, a gene overlap graph was constructed by defining an edge between orthologous groups if the intersection of their associated sets of parent genes is at least 50\% of the smaller of the two. Gene groups were then taken as the connected components of the resulting graph, yielding 14,909 groups. This is commensurate with the roughly 15,000 genes in each genome, which suggests this approach has successfully clustered orthologous groups derived from a common set of parent genes.
